### 2018-11-20 Sections/protocols_for_the_quantum_internet.tex
Wstate QEC

\comment{Show mathematical results}

>>>>

\comment{Complete}

\begin{align}
\ket\psi_L &= \alpha\ket{0}+\beta\ket{1},\nonumber\\
\alpha &= \cos \left(\frac{\theta}{2}\right),\nonumber\\
\beta &= e^{i\phi}\sin \left(\frac{\theta}{2}\right).
\end{align}

\begin{align}
P_H &=1-e^{-t/T_1} + e^{-t/T_1}(e^{-t/T_2} + \frac{2}{N}(1-e^{-t/T_2})),\nonumber\\ 
F_H &= e^{-t/T_1}\frac{e^{-t/T_2} + (1-e^{-t/T_2})\left(\frac{2+\sin^2\theta}{2N}\right)}{e^{-t/T_2}+\frac{2}{N}(1-e^{-t/T_2})}.	
\end{align}

Fig.~\ref{fig:W_state_QEC_fidelity} illustrates the fidelity of an error-corrected logical qubit using W-state encoding.

\begin{figure}[!htbp]
\if 2\pubmode
	\includegraphics[clip=true, width=0.475\textwidth]{W_state_QEC_prob}\\
	\includegraphics[clip=true, width=0.475\textwidth]{W_state_QEC_fidelity}
\else
	\includegraphics[clip=true, width=0.475\textwidth]{W_state_QEC_prob}
	\includegraphics[clip=true, width=0.475\textwidth]{W_state_QEC_fidelity}
\fi
\caption{\comment{Get vector versions. Both 3D plots.}}\label{fig:W_state_QEC_fidelity}
\end{figure}
